---
title: "Yet Another COVID19 Projection"
output: 
  html_notebook: 
    code_folding: hide
    fig_caption: yes
    fig_width: 9
---

```{r include=FALSE}
library(lubridate)
```

*Last update `r today()`*

Projection for the next X days in several countries using a SEIRQRDP model based on [Peng et al. 2020](https://arxiv.org/pdf/2002.06563.pdf).
Code adapted (barely) from matlab [E. Cheynet's code](https://la.mathworks.com/matlabcentral/fileexchange/74545-generalized-seir-epidemic-model-fitting-and-computation)

Source code at [github](https://github.com/harpomaxx/COVID19/tree/master/SEIQRDP)

**DISCLAIMER** Dot not consider these projections seriously. I'm far from being an expert on this field. They were made just for testing and fun. 

```{r warning=FALSE, include=FALSE}
source("SEIQRDP.R")
LT <- 5    #1-14 days, latent time in days, incubation period, gamma^(-1)   
QT <- 5  #Quarantine time in days, recovery time, infectious period, delta^(-1)
alpha_guess <- 1.0
beta_guess <- 1.0
gamma_guess <- 1 / LT
delta_guess <- 1 / QT
kappa_guess <- 0.01 #dead rate
lambda_guess <- 0.08 # recover rate

start_date<-(today()-15) 
fitted_date<-(start_date+15) 
start_date <- start_date %>% format('%m-%d-%Y')
fitted_date <- fitted_date %>% format('%m-%d-%Y')
```

# Argentina
```{r message=FALSE, warning=FALSE}
LT <- 10    #1-14 days, latent time in days, incubation period, gamma^(-1)   
QT <- 7  #Quarantine time in days, recovery time, infectious period, delta^(-1)
alpha_guess <- 1.0
beta_guess <- 1.0
gamma_guess <- 1 / LT
delta_guess <- 1 / QT
kappa_guess <- 0.01 #dead rate
lambda_guess <- 0.5 # recover rate
region = "Argentina"
population =  40e6

data<-get_jhu_data(region=region,population = population )
#data$cumulative_incidence$infected_cases<-unlist(data$cumulative_incidence[,2] *5)
#data$cumulative_incidence$recovered_cases<-unlist(data$cumulative_incidence[,3] *5)


data_fit<-create_fit_data(data,fitted_date = fitted_date,start_date = start_date)
parameters<-c(alpha_guess,beta_guess,gamma_guess,delta_guess,kappa_guess,lambda_guess)



params<-SEIQRDP_fit(parameters,data_fit)
forecast <-61
forecast_data <- SEIQRDP_predict(forecast,params,data_fit,data)
plot_arg<-SEIQRDP_plot(forecast_data,region)


plot_arg 

```

# Brazil
```{r message=FALSE, warning=FALSE}
region="Brazil"
population=21e7

start_date<-(today()-15) 
fitted_date<-(start_date+14) 
start_date <- start_date %>% format('%m-%d-%Y')
fitted_date <- fitted_date %>% format('%m-%d-%Y')


data<-get_jhu_data(region=region,population = population )
data_fit<-create_fit_data(data,fitted_date = fitted_date,start_date = start_date)
parameters<-c(alpha_guess,beta_guess,gamma_guess,delta_guess,kappa_guess,lambda_guess)
params<-SEIQRDP_fit(parameters,data_fit)
forecast <-30
forecast_data <- SEIQRDP_predict(forecast,params,data_fit,data)
plot<-SEIQRDP_plot(forecast_data,region)
plot
```

# Italy

```{r message=FALSE, warning=FALSE}
start_date<-(today()-18) 
fitted_date<-(start_date+15) 
start_date <- start_date %>% format('%m-%d-%Y')
fitted_date <- fitted_date %>% format('%m-%d-%Y')
region ="Italy"
population=61e6
data<-get_jhu_data(region=region,population = population )
data_fit<-create_fit_data(data,fitted_date = fitted_date,start_date = start_date)
parameters<-c(alpha_guess,beta_guess,gamma_guess,delta_guess,kappa_guess,lambda_guess)
params<-SEIQRDP_fit(parameters,data_fit)
forecast <-30
forecast_data <- SEIQRDP_predict(forecast,params,data_fit,data)
plot<-SEIQRDP_plot(forecast_data,region)

plot
```

#Spain
```{r message=FALSE, warning=FALSE}


region = "Spain"
population = 46e6

data<-get_jhu_data(region=region,population = population )
data_fit<-create_fit_data(data,fitted_date = fitted_date,start_date = start_date)
parameters<-c(alpha_guess,beta_guess,gamma_guess,delta_guess,kappa_guess,lambda_guess)
params<-SEIQRDP_fit(parameters,data_fit)
forecast <-30
forecast_data <- SEIQRDP_predict(forecast,params,data_fit,data)
plot<-SEIQRDP_plot(forecast_data,region)

plot
```
# Chile
```{r message=FALSE, warning=FALSE}
region ="Chile"
population=18e6
data<-get_jhu_data(region=region,population = population )
data_fit<-create_fit_data(data,fitted_date = fitted_date,start_date = start_date)
parameters<-c(alpha_guess,beta_guess,gamma_guess,delta_guess,kappa_guess,lambda_guess)
params<-SEIQRDP_fit(parameters,data_fit)
forecast <-61
forecast_data <- SEIQRDP_predict(forecast,params,data_fit,data)
plot_chile<-SEIQRDP_plot(forecast_data,region)

plot_chile
```

#Korea

```{r message=FALSE, warning=FALSE}
region ="Korea, South"
population=60e6
data<-get_jhu_data(region=region,population = population )
data_fit<-create_fit_data(data,fitted_date = fitted_date,start_date = start_date)
parameters<-c(alpha_guess,beta_guess,gamma_guess,delta_guess,kappa_guess,lambda_guess)
params<-SEIQRDP_fit(parameters,data_fit)
forecast <-30
forecast_data <- SEIQRDP_predict(forecast,params,data_fit,data)
plot<-SEIQRDP_plot(forecast_data,region)

plot
```


